```{r setup, cache = F, echo = F, message = F,include=F,results='hide', warning = F, tidy = F}
# make this an external chunk that can be included in any file
opts_chunk$set(message = T, error = T, warning = T, comment = NA, fig.align = 'center', dev="CairoPNG",
  		   dpi = 96, tidy = F, cache = F,echo=T,include=F, cache.path = '.cache/',
			   fig.path = 'fig/',fig.height=5,fig.width=10, par(pch=19))

options(xtable.type = 'html', width=68,digits=1, show.signif.stars=FALSE)

# Evaluate the figure caption after the plot
opts_knit$set(eval.after='fig.cap')

# Avoid including base64_images - this only 
# works with the .RProfile setup
options(base64_images = "none")

# Use the table counter that the htmlTable() provides
options(table_counter = TRUE)

# Use the figure counter that we declare below
options(figure_counter = TRUE)
# Use roman letters (I, II, III, etc) for figures
#options(figure_counter_roman = TRUE)

# Adding the figure number is a little tricky when the format is roman
getNextFigureNo <- function() as.character(as.numeric(options("figure_counter")))

# Add a figure counter function
knit_hooks$set(plot = function(x, options) {
  fig_fn = paste0(opts_knit$get("base.url"), 
                  paste(x, collapse = "."))
 
  # Some stuff from the default definition
  fig.cap <- knitr:::.img.cap(options)
 
  # Style and additional options that should be included in the img tag
  style=c("display: block",
          sprintf("margin: %s;",
                   switch(options$fig.align, 
                          left = 'auto auto auto 0', 
                          center = 'auto',
                          right = 'auto 0 auto auto')))
  # Certain arguments may not belong in style, 
  # for instance the width and height are usually
  # outside if the do not have a unit specified
  addon_args = ""
 
  # This is perhaps a little overly complicated prepared 
  # with the loop but it allows for a more out.parameters if necessary
  if (any(grepl("^out.(height|width)", names(options)))){
      on <- names(options)[grep("^out.(height|width)", names(options))]
      for(out_name in on){
          dimName <- substr(out_name, 5, nchar(out_name))
          if (grepl("[0-9]+(em|px|%|pt|pc|in|cm|mm)", out_name))
              style=append(style, paste0(dimName, ": ", options[[out_name]]))
          else if (length(options$out.width) > 0)
              addon_args = paste0(addon_args, dimName, "='", options[[out_name]], "'")
      }
  }
 
  # Add counter if wanted
  fig_number_txt <- ""
  cntr <- getOption("figure_counter", FALSE)
  if (cntr != FALSE){
    if (is.logical(cntr))
      cntr <- 1
    # The figure_counter_str allows for custom 
    # figure text, you may for instance want it in
    # bold: <b>Figure %s:</b>
    # The %s is so that you have the option of setting the
    # counter manually to 1a, 1b, etc if needed
    fig_number_txt <- 
      sprintf(getOption("figure_counter_str", "Figure %s: "), 
              ifelse(getOption("figure_counter_roman", FALSE), 
                     as.character(as.roman(cntr)), as.character(cntr)))
 
    if (is.numeric(cntr))
      options(figure_counter = cntr + 1)
  }
 
  # Put it all together
  paste0("<figure><img src='", fig_fn, "'", 
         " ", addon_args,
         paste0(" style='", paste(style, collapse="; "), "'"),
         ">",
         "<figcaption>", fig_number_txt, fig.cap, "</figcaption></figure>")
})

knit_hooks$set(inline = function(x) {
  if(is.numeric(x)) {
    round(x, getOption('digits'))
  } else {
    paste(as.character(x), collapse = ', ')
  }
})
knit_hooks$set(plot = knitr:::hook_plot_html)
library(knitr); library(knitcitations)
bib <- read.bibtex("rrmda.bib")
cite_options(tooltip = FALSE, linked = TRUE,
    numerical = TRUE, bibtex_data = FALSE)
#
#Reading in your own bib file:
#bib <- read.bibtex(file.path(getwd(), "Presentation", basename(getOption("bib.loc"))))
#cite in text using `r citet(bib[1])`
```

```{r mainLibr}

library(Hmisc)
library(reshape)
library(survival)
require(openintro)
library(car)
library(psych)
library(ggplot2)
library(lattice)
require(mosaic)
require(xtable)
library(RColorBrewer)
library(rms) # I use the cox regression from this package
library(boot) # The melanoma data set is used in this exampe
library(Gmisc) # Stuff I find convenient
trellis.par.set(theme=col.mosaic())  # get a better color scheme for lattice
source("~/Dropbox/R_Scripts/glob_r_scr/print_pval.R")
source("~/Dropbox/R_Scripts/glob_r_scr/median_range.R")

```


```{r loadData}
source("code/data_prep.R")
```

```{r Versions}
sessionInfo()
```

This is a Reproducable researche Rmarkdow example: Mortalty in USA Hospitals
========================================================



**Abstract**


__Objective__
Create a reproducable research article with Rmarkdown. I will be using data from [Medicare](http://hospitalcompare.hhs.gov).
I will be using Knitr `r citep(bib["knitr_man"])` for Rmarkdown compilation.

__Methods__


__Results__


__Conlutions__

Introduction
------------
This is how to cite in knitr with knitrcitations `r citep(bib["bentall_technique_1968"])`. 


Material and methods
------------
This is the first table __Table__ 1.







```{r plot1, fig.height=3, fig.width=9,include=TRUE, fig.cap="A histogram and density estimates for three outcomes."}
cols <- brewer.pal(9,"Blues")
pal <- colorRampPalette(cols)
par(mfrow=c(1,3))
hist(outcome[,11],xlab="30-day Death Rate",
     main=substitute(bar(X)==k,list(k=mean(outcome[,11],na.rm=TRUE))),xlim=c(0,20),prob=TRUE,col=pal(20))
lines(density(outcome[,11],na.rm=TRUE),col="red")             # add a density estimate with defaults
abline(v=median(outcome[,11],na.rm=TRUE),col="blue")
abline(h=0)
hist(outcome[,17],xlab="30-day Death Rate",
     main=substitute(bar(X)==k,list(k=mean(outcome[,17],na.rm=TRUE))),xlim=c(0,20),prob=TRUE,col=pal(20))
lines(density(outcome[,17],na.rm=TRUE),col="red") 
abline(v=median(outcome[,17],na.rm=TRUE),col="blue")
abline(h=0)
hist(outcome[,23],xlab="30-day Death Rate",
     main=substitute(bar(X)==k,list(k=mean(outcome[,23],na.rm=TRUE))),xlim=c(0,20),prob=TRUE,col=pal(20))
lines(density(outcome[,23],na.rm=TRUE),col="red") 
abline(v=median(outcome[,23],na.rm=TRUE),col="blue")
abline(h=0)
```

As you can deduce from the Figure `r getNextFigureNo()`.

```{r plot2, fig.height=6, fig.width=7,include=TRUE, fig.cap="A boxplot of median moratlity accross the regeons."}
outcome2 <- outcome[!(outcome$State %in% names(table(outcome$State)[table(outcome$State)<20])),]
death <- outcome2[, 11]
state <- outcome2$State
par(las=2,cex.axis=0.8)
state.median<-reorder(state,death, na.rm=T,median)
par(las=2,cex.axis=0.8)
state.median<-reorder(state,death, na.rm=T,median)
boxplot(death ~ state.median,ylab="30-day Death Rate",main="Heart Attack 30-day Death Rate by State",xaxt="n")
labs <- paste0(names(table(state.median)),"(",as.numeric(table(state.median)),")")
axis(side=1,at=1:length(levels(state.median)),lab=FALSE)
text(1:length(levels(state.median)),par("usr")[3] - 1.5,srt=90, labels=labs, xpd=T, cex=0.7)
```
There is other image here Figure `r getNextFigureNo()`
